Supplementary Information: Drought sensitivity is not a species trait: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-09-04 doc/response_to_reviewer_R1.Rmd

1 Line 175 “Using the late wet/early dry dendrometer…” Since there were two time of censuses (January and June) for the measurement, can the author clarify which time do they use to calculate the annual growth? Based on the measurement of January or June?

**RESPONSE: The January measurement was used to calculate annual growth. We have now included this detail at in now reads:  
"Using the late wet/early dry dendrometer band censuses (centred around January), we calculated annualised growth for each tree and year from 2009 to 2022."**

2 The topographic wetness index. Are there any measured soil moisture data in this plot? Since this index is only based on topography, it will be good if the author could provide some measured soil moisture data to calibrate the prediction based on model prediction.

**RESPONSE: Unfortunately soil moisture data from the plot is not available for the years of study across which dendroband data are available. HKK, being fairly remote, has limited access to power sources and other infrastructure that are needed to maintain such data collection. We are currently piloting a few basic soil moisture sensors, however, this will have limited value for calibration as they only measure the top layer of the soil and are limited in spatial scale compared to the spatial resolution of TWI data.**

@@

Fig. S1 What does the shade area indicate? The three different drought events?

**RESPONSE: Yes, the shaded area indicates the three different drought years. We have edited the text to reflect this.**

Fig S6 The R Square is too low, so it is difficult to detect the linear relationship. The same issue for Fig. S11 and Fig. S12. For the non-significant correlation, it’s better use dashed lines instead of solid line.

**RESPONSE: Thanks for this suggestion. The ditted line in Fig S6 was originally the 1:1 line - a strict null expectation. We have now added dashed lines for the significant correlations. Following the same logic, for S11 and S12, we have now changed the non-significant correlations to dashed lines.**

### 2025-09-04 doc/supplementary_information.Rmd
updated SI doc with new figs

---
title: "Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments"
author: 
date: 
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: growth-precip-thailand.bib
suppress-bibliography: false
csl: new-phytologist.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

![**Figure S8:** Calculated Topographic Wetness Index (TWI) values for the HKK plot](display/explore/twi.png)

![**Figure S9:** Distribution of DBH with Crown Illumination Index (CII) in 2014.](display/explore/dbh_cii.png)

@@

![**Figure S13:** Testing correlations for DBH $\perp\!\!\!\perp$ TWI by species](display/explore/cond_dep_dbh_twi.png)

![**Figure S14:** Testing correlations for CII $\perp\!\!\!\perp$ TWI by species](display/explore/cond_dep_cii_twi.png)

>>>>

---
title: "Supplementary Information: Drought sensitivity is not a species trait: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments"
author: 
date: 
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: growth-precip-thailand.bib
suppress-bibliography: false
csl: new-phytologist.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

@@

![**Figure S8:** Calculated Topographic Wetness Index (TWI) values for the HKK plot](display/twi.png)

![**Figure S9:** Distribution of DBH with Crown Illumination Index (CII) in 2014.](display/dbh_cii.png)

@@

![**Figure S13:** Testing correlations for DBH $\perp\!\!\!\perp$ TWI by species](display/cond_dep_dbh_twi.png)

![**Figure S14:** Testing correlations for CII $\perp\!\!\!\perp$ TWI by species](display/cond_dep_cii_twi.png)
